The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Addition.tex
Update Addition.tex

@@

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, it's important to know the things that come with being on such a platform and the possible influences those things might have on the method.\\\\
In day-to-day usage of online platforms and services it's not uncommon to face some issues, whether it's execution, connectivity and so on. E-Learning-platforms are not particularly different to those. Therefore, we want to discuss, in this paper, to which extent these problems can influence the test-results of being on such a 'issue-infected' platform in contrast to a well running platform with no issues.\\\\
We tried to focus on the most frequent issues we faced in our experience of browsing on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\

@@

\section{Discussion}
\section{Conclusion}
\section{References}
\url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}
\end{document}

>>>>

Skip to content
Search or jump to…

Pull requests
Issues
Marketplace
Explore

@mevv2 
UebeI2lauf
/
insertcreativeName
1
00
Code
Issues
Pull requests
Actions
Projects
Wiki
Security
Insights
insertcreativeName/Addition.tex
@mevv2
mevv2 Update Addition.tex
Latest commit e7bd3b9 now
 History
 1 contributor
109 lines (96 sloc)  4.99 KB

@@

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, 
It's important to know the things that come with being on such a platform and the 
possible influences those things might have on the method.\\\\
In day-to-day usage of online platforms and services it's not uncommon to face some 
issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
particularly different to those. Therefore, we want to discuss, in this paper, to 
which extent these problems can influence the test-results of being on such an 
'issue-infected' platform in contrast to a well running platform with no issues.\\\\
We tried to focus on the most frequent issues we faced in our experience of browsing 
on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors', because things like lagging or 100ms more or less ping time are in our case of mostly texts and pictures not as important as those client errors.\\\\

@@

\section{Discussion}
As we can see, the results show not much significance under our circumstances.Even though we cannot a significance, we can see slight worsening of the average scores in the error groups than to the control group. But we don't have to forget, that this was a short term test (for example 1 hour) and we didn't include that many variables like time, age and so on. Having such problem-infected websites and platforms can be very frustrating in the long run. Unfortunately, we couldn't recreate this scenario. It would be very interesting to see, how much significance such things like errors will show  in a long run with more variables included.           
\section{Conclusion}
\section{References}
\url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}
\end{document}
